---
title: "rocauc"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(dplyr)
library(stringr)
library(purrr)
library(RVenn)
library(ggplot2)
library(ggVennDiagram)
library(VennDiagram)
library(cutpointr)

library(dplyr)
library(tidyr)
```



```{r}
FDG_SUVR  <- read_excel("~/Downloads/FDG_SUVR.xlsx")
Amyloid_SUVR <- read_excel("~/Downloads/Amyloid_SUVR.xlsx")
Tau_SUVR  <- read_excel("~/Downloads/Tau_SUVR.xlsx")
 
#Tau_0926 <- na.omit(Tau_0926, cols=c("DX", "APOE4","EXAMDATE"))
```


```{r}
TABLE<-data.frame(table(Amyloid_SUVR$PTID))
Amyloid_first<- as.data.frame(matrix(0,nrow(TABLE), ncol(Amyloid_SUVR)))
Amyloid_last<- as.data.frame(matrix(0,nrow(TABLE), ncol(Amyloid_SUVR)))
for (i in 1:nrow(TABLE)){
Amyloid_first[i,] <- Amyloid_SUVR[min(which(Amyloid_SUVR$PTID == TABLE$Var1[i])), ]

Amyloid_last[i,] <- Amyloid_SUVR[max(which(Amyloid_SUVR$PTID == TABLE$Var1[i])), ]

}

colnames(Amyloid_first)<-colnames(Amyloid_SUVR)
colnames(Amyloid_last)<-colnames(Amyloid_SUVR)
```

```{r}
SIGN_Tau0<-na.omit(Tau_SUVR, cols=c("DX","EXAMDATE"))
SIGN_Amyloid0<-na.omit(Amyloid_last, cols=c("DX","EXAMDATE"))
SIGN_FDG0<-na.omit(FDG_SUVR, cols=c("DX","EXAMDATE"))
 
SIGN_FDG0<-SIGN_FDG0[SIGN_FDG0$DX %in% c("AD", "CN", "EMCI", "LMCI", "SMC" ),]
SIGN_Tau0<-SIGN_Tau0[SIGN_Tau0$DX %in% c("AD", "CN", "EMCI", "LMCI", "SMC" ),]
SIGN_Amyloid0<-SIGN_Amyloid0[SIGN_Amyloid0$DX %in% c("AD", "CN", "EMCI", "LMCI", "SMC" ),]

```

```{r}
SIGN_Amyloid0$AD<-SIGN_Amyloid0$DX
summary(as.factor(SIGN_Amyloid0$DX))
```


```{r}
for (i in 1:nrow(SIGN_Amyloid0)){
  if (SIGN_Amyloid0[i,4]=="LMCI"  )  {
    SIGN_Amyloid0[i,4]="AD"
  }
  else if (SIGN_Amyloid0[i,4]=="EMCI") {
    SIGN_Amyloid0[i,4]="CN"
  }
  else if (SIGN_Amyloid0[i,4]=="SMC") {
    SIGN_Amyloid0[i,4]="CN"
  }
}
summary(as.factor(SIGN_Amyloid0$DX))
 
SIGN_Tau0$AD<-SIGN_Tau0$DX
summary(as.factor(SIGN_Tau0$DX))

for (i in 1:nrow(SIGN_Tau0)){
  if (SIGN_Tau0[i,4]=="LMCI"  )  {
    SIGN_Tau0[i,4]="AD"
  }
  else if (SIGN_Tau0[i,4]=="EMCI") {
    SIGN_Tau0[i,4]="CN"
  }
  else if (SIGN_Tau0[i,4]=="SMC") {
    SIGN_Tau0[i,4]="CN"
  }
}
summary(as.factor(SIGN_Tau0$DX))
 
SIGN_FDG0$AD<-SIGN_FDG0$DX
summary(as.factor(SIGN_FDG0$DX))

for (i in 1:nrow(SIGN_FDG0)){
  if (SIGN_FDG0[i,4]=="LMCI"  )  {
    SIGN_FDG0[i,4]="AD"
  }
  else if (SIGN_FDG0[i,4]=="EMCI") {
    SIGN_FDG0[i,4]="CN"
  }
  else if (SIGN_FDG0[i,4]=="SMC") {
    SIGN_FDG0[i,4]="CN"
  }
}
summary(as.factor(SIGN_FDG0$DX))
```



```{r}
 #test_fdg$MEAN<-apply(test_fdg[,c(12:159)], 1, mean)

SIGN_Tau0$MEAN<-apply(SIGN_Tau0[,c(12:159)], 1, mean)
SIGN_Amyloid0$MEAN<-apply(SIGN_Amyloid0[,c(12:159)], 1, mean)
SIGN_FDG0$MEAN<-apply(SIGN_FDG0[,c(12:159)], 1, mean)
```
 

```{r}
df<-SIGN_FDG0[which(SIGN_FDG0$AD %in% c("CN", "AD") ),]
cp_fdg <- cutpointr( df, MEAN, AD, 
                method = oc_youden_normal, metric = youden)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_fdg)

plot(cp_fdg)

```
```{r}
df<-SIGN_Amyloid0[which(SIGN_Amyloid0$AD %in% c("CN", "AD") ),]
cp_amy <- cutpointr( df, MEAN, AD, 
                method = oc_youden_normal, metric = youden)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_amy)

plot(cp_amy)


```


```{r}
df<-SIGN_Tau0[which(SIGN_Tau0$AD %in% c("CN", "AD") ),]
cp_tau <- cutpointr(df, MEAN, AD, 
                method = oc_youden_normal, metric = youden)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_tau)

plot(cp_tau)


```





 
Positive Predictive Value PPV = true positives / total positives (true and false)
Negative Predictive Value NPV = true negatives / total negatives (true and false)
```{r}
SIGN_FDG0<-SIGN_FDG0[SIGN_FDG0$DX %in% c("AD", "CN"),]
SIGN_Tau0<-SIGN_Tau0[SIGN_Tau0$DX %in% c("AD", "CN"),]
SIGN_Amyloid0<-SIGN_Amyloid0[SIGN_Amyloid0$DX %in% c("AD", "CN" ),]
```

```{r}
 #test_fdg$MEAN<-apply(test_fdg[,c(12:159)], 1, mean)

SIGN_Tau0$MEAN<-apply(SIGN_Tau0[,c(12:159)], 1, mean)
SIGN_Amyloid0$MEAN<-apply(SIGN_Amyloid0[,c(12:159)], 1, mean)
SIGN_FDG0$MEAN<-apply(SIGN_FDG0[,c(12:159)], 1, mean)
```
 

```{r}
df<-SIGN_FDG0[which(SIGN_FDG0$AD %in% c("CN", "AD") ),]
cp_fdg <- cutpointr( df, MEAN, AD, 
                method = oc_youden_normal, metric = youden)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_fdg)

plot(cp_fdg)

```
```{r}
df<-SIGN_Amyloid0[which(SIGN_Amyloid0$AD %in% c("CN", "AD") ),]
cp_amy <- cutpointr( df, MEAN, AD, 
                method = oc_youden_normal, metric = youden)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_amy)

plot(cp_amy)


```


```{r}
df<-SIGN_Tau0[which(SIGN_Tau0$AD %in% c("CN", "AD") ),]
cp_tau <- cutpointr(df, MEAN, AD, 
                method = oc_youden_normal, metric = youden)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_tau)

plot(cp_tau)


```









# Performance per 148 node
```{r}
auc_performance<- as.data.frame(matrix(0,148,3))

SIGN_Tau0<-na.omit(Tau_SUVR, cols=c("DX","EXAMDATE"))
SIGN_Amyloid0<-na.omit(Amyloid_SUVR, cols=c("DX","EXAMDATE"))
SIGN_FDG0<-na.omit(FDG_SUVR, cols=c("DX","EXAMDATE"))
 
SIGN_FDG0<-SIGN_FDG0[SIGN_FDG0$DX %in% c("AD", "CN", "EMCI", "LMCI", "SMC" ),]
SIGN_Tau0<-SIGN_Tau0[SIGN_Tau0$DX %in% c("AD", "CN", "EMCI", "LMCI", "SMC" ),]
SIGN_Amyloid0<-SIGN_Amyloid0[SIGN_Amyloid0$DX %in% c("AD", "CN", "EMCI", "LMCI", "SMC" ),]

```

```{r}
for (i in 1:nrow(SIGN_Amyloid0)){
  if (SIGN_Amyloid0[i,4]=="LMCI"  )  {
    SIGN_Amyloid0[i,4]="AD"
  }
  else if (SIGN_Amyloid0[i,4]=="EMCI") {
    SIGN_Amyloid0[i,4]="CN"
  }
  else if (SIGN_Amyloid0[i,4]=="SMC") {
    SIGN_Amyloid0[i,4]="CN"
  }
}

for (i in 1:nrow(SIGN_Tau0)){
  if (SIGN_Tau0[i,4]=="LMCI"  )  {
    SIGN_Tau0[i,4]="AD"
  }
  else if (SIGN_Tau0[i,4]=="EMCI") {
    SIGN_Tau0[i,4]="CN"
  }
  else if (SIGN_Tau0[i,4]=="SMC") {
    SIGN_Tau0[i,4]="CN"
  }
}


for (i in 1:nrow(SIGN_FDG0)){
  if (SIGN_FDG0[i,4]=="LMCI"  )  {
    SIGN_FDG0[i,4]="AD"
  }
  else if (SIGN_FDG0[i,4]=="EMCI") {
    SIGN_FDG0[i,4]="CN"
  }
  else if (SIGN_FDG0[i,4]=="SMC") {
    SIGN_FDG0[i,4]="CN"
  }
}

```
```{R}

for (i in 1:148){

  SIGN_Tau0$MEAN<-apply(SIGN_Tau0[,11+i],1,mean)
  SIGN_Amyloid0$MEAN<-apply(SIGN_Amyloid0[,11+i],1,mean)
  SIGN_FDG0$MEAN<-apply(SIGN_FDG0[,11+i],1,mean)


  cp_amy <- cutpointr(SIGN_Amyloid0, MEAN, DX,  direction = ">=", pos_class = "AD", method = oc_youden_normal, metric = youden)
  cp_tau <- cutpointr(SIGN_Tau0, MEAN, DX,  direction = ">=", pos_class = "AD", method = oc_youden_normal, metric = youden)
  cp_fdg <- cutpointr(SIGN_FDG0, MEAN, DX,  direction = ">=", pos_class = "AD", method = oc_youden_normal, metric = youden)
  auc_performance[i,1]<-summary(cp_amy)$cutpointr[[1]]$AUC
  auc_performance[i,2]<-summary(cp_tau)$cutpointr[[1]]$AUC
  auc_performance[i,3]<-summary(cp_fdg)$cutpointr[[1]]$AUC
  
}



```

```{r}
ggplot(auc_performance, aes(1:148)) + 
  geom_smooth(aes(y = V1, colour = "Amyloid")) + 
  geom_smooth(aes(y = V2, colour = "Tau"))+
  geom_smooth(aes(y = 1-V3, colour = "FDG"))+
  ylab("AUC")+
  xlab("Node 1~148")

```
### see anyone here

# Performance per 148 node
```{r}
auc_performance<- as.data.frame(matrix(0,148,3))

SIGN_Tau0<-na.omit(Tau_SUVR, cols=c("DX","EXAMDATE"))
SIGN_Amyloid0<-na.omit(Amyloid_SUVR, cols=c("DX","EXAMDATE"))
SIGN_FDG0<-na.omit(FDG_SUVR, cols=c("DX","EXAMDATE"))
 
SIGN_FDG0<-SIGN_FDG0[SIGN_FDG0$DX %in% c("AD", "CN", "EMCI", "LMCI", "SMC" ),]
SIGN_Tau0<-SIGN_Tau0[SIGN_Tau0$DX %in% c("AD", "CN", "EMCI", "LMCI", "SMC" ),]
SIGN_Amyloid0<-SIGN_Amyloid0[SIGN_Amyloid0$DX %in% c("AD", "CN", "EMCI", "LMCI", "SMC" ),]

```

```{r}
for (i in 1:nrow(SIGN_Amyloid0)){
  if (SIGN_Amyloid0[i,4]=="LMCI"  )  {
    SIGN_Amyloid0[i,4]="AD"
  }
  else if (SIGN_Amyloid0[i,4]=="EMCI") {
    SIGN_Amyloid0[i,4]="CN"
  }
  else if (SIGN_Amyloid0[i,4]=="SMC") {
    SIGN_Amyloid0[i,4]="CN"
  }
}

for (i in 1:nrow(SIGN_Tau0)){
  if (SIGN_Tau0[i,4]=="LMCI"  )  {
    SIGN_Tau0[i,4]="AD"
  }
  else if (SIGN_Tau0[i,4]=="EMCI") {
    SIGN_Tau0[i,4]="CN"
  }
  else if (SIGN_Tau0[i,4]=="SMC") {
    SIGN_Tau0[i,4]="CN"
  }
}


for (i in 1:nrow(SIGN_FDG0)){
  if (SIGN_FDG0[i,4]=="LMCI"  )  {
    SIGN_FDG0[i,4]="AD"
  }
  else if (SIGN_FDG0[i,4]=="EMCI") {
    SIGN_FDG0[i,4]="CN"
  }
  else if (SIGN_FDG0[i,4]=="SMC") {
    SIGN_FDG0[i,4]="CN"
  }
}

```
```{R}

for (i in 1:148){

  SIGN_Tau0$MEAN<-apply(SIGN_Tau0[,11+i],1,mean)
  SIGN_Amyloid0$MEAN<-apply(SIGN_Amyloid0[,11+i],1,mean)
  SIGN_FDG0$MEAN<-apply(SIGN_FDG0[,11+i],1,mean)


  cp_amy <- cutpointr(SIGN_Amyloid0, MEAN, DX,  direction = ">=", pos_class = "AD", method = oc_youden_normal, metric = youden)
  cp_tau <- cutpointr(SIGN_Tau0, MEAN, DX,  direction = ">=", pos_class = "AD", method = oc_youden_normal, metric = youden)
  cp_fdg <- cutpointr(SIGN_FDG0, MEAN, DX,  direction = ">=", pos_class = "AD", method = oc_youden_normal, metric = youden)
  auc_performance[i,1]<-summary(cp_amy)$cutpointr[[1]]$optimal_cutpoint
  auc_performance[i,2]<-summary(cp_tau)$cutpointr[[1]]$optimal_cutpoint
  auc_performance[i,3]<-summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
  
}



```

## check for whether it is AD or NC
```{r}
Amyloid_perfromance<- as.data.frame(matrix(0,nrow(SIGN_Amyloid0),149))
Tau_perfromance<- as.data.frame(matrix(0,nrow(SIGN_Tau0),149))
FDG_perfromance<- as.data.frame(matrix(0,nrow(SIGN_FDG0),149))
Amyloid_perfromance$V1<-SIGN_Amyloid0$PTID
Tau_perfromance$V1<-SIGN_Tau0$PTID
FDG_perfromance$V1<-SIGN_FDG0$PTID

```

## for loop for ad
```{r}
for (i in 1:148){

  Amyloid_perfromance[,i+1]<-as.numeric(SIGN_Amyloid0[,11+i]>auc_performance[i,1]) ## 1 is AD ## 0 is NC
  Tau_perfromance[,i+1]<-as.numeric(SIGN_Tau0[,11+i]>auc_performance[i,2]) ## 1 is AD ## 0 is NC
  FDG_perfromance[,i+1]<-as.numeric(SIGN_FDG0[,11+i]<auc_performance[i,3]) ## 0 is AD ## 1 is NC
}

```

```{r}
a<-as.data.frame(rowSums(Amyloid_perfromance[,2:149]))
b<-as.data.frame(rowSums(Tau_perfromance[,2:149]))
c<-as.data.frame(rowSums(FDG_perfromance[,2:149]))

a<-cbind(a,1:2628)
b<-cbind(b,1:537)
c<-cbind(c,1:3405)
```


```{r}
a[,2]<-as.numeric(a[,1]>74) ## 1 is AD ## 0 is NC
b[,2]<-as.numeric(b[,1]>74) ## 1 is AD ## 0 is NC
c[,2]<-as.numeric(c[,1]<74) ## 0 is AD ## 1 is NC
```
##back to rejoin
```{r}
SIGN_Amyloid0$newmodel <- a$`1:2628`
SIGN_Tau0$newmodel <- b$`1:537`
SIGN_FDG0$newmodel <-c$`1:3405`


```


```{r}
df<-SIGN_FDG0[which(SIGN_FDG0$newmodel %in% c("1", "0") ),]
cp_fdg <- cutpointr( df, MEAN, newmodel, 
                method = oc_youden_normal, metric = youden)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_fdg)

plot(cp_fdg)

```
```{r}
df<-SIGN_Amyloid0[which(SIGN_Amyloid0$newmodel %in% c("1", "0") ),]
cp_amy <- cutpointr( df, MEAN, newmodel, 
                method = oc_youden_normal, metric = youden)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_amy)

plot(cp_amy)


```


```{r}
df<-SIGN_Tau0[which(SIGN_Tau0$newmodel %in% c("1", "0") ),]
cp_tau <- cutpointr(df, MEAN, newmodel, 
                method = oc_youden_normal, metric = youden)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_tau)

plot(cp_tau)


```







for (i in nrow(Amyloid_perfromance)){
  if(Amyloid_perfromance[i,1]<74){
    a[i,2] = "NC"
  } else {
    a[i,2] = "AD"
  }
}


for (i in nrow(Tau_perfromance)){
  if(Tau_perfromance[i,1]<74){
    b[i,2] = "NC"
  } else {
    b[i,2] = "AD"
  }
}

for (i in nrow(FDG_perfromance)){
  if(FDG_perfromance[i,1]>74){
    c[i,2] = "NC"
  } else {
    c[i,2] = "AD"
  }
}
```


```{r}
 #test_fdg$MEAN<-apply(test_fdg[,c(12:159)], 1, mean)

SIGN_Tau0$MEAN<-apply(SIGN_Tau0[,c(12:159)], 1, mean)
SIGN_Amyloid0$MEAN<-apply(SIGN_Amyloid0[,c(12:159)], 1, mean)
SIGN_FDG0$MEAN<-apply(SIGN_FDG0[,c(12:159)], 1, mean)
```
 

```{r}
df<-SIGN_FDG0[which(SIGN_FDG0$AD %in% c("CN", "AD") ),]
cp_fdg <- cutpointr( df, MEAN, DX, 
                method = maximize_metric, metric = sum_sens_spec)
#summary(cp_fdg)$cutpointr[[1]]$optimal_cutpoint
summary(cp_fdg)

```